### 2022-05-31 ms.tex
setting up the repo

\documentclass[12pt]{article}

@@

<<debug,echo=F>>=
run_level <- 1
if(is.numeric(run_level)){
  lik_run_level <- run_level
}
@

@@

<<knitr_setup,include=FALSE,cache=FALSE,purl=FALSE,child="header.Rnw">>=
@

<<doParallel,include=F,cache=F>>=
cores <-  as.numeric(Sys.getenv('SLURM_NTASKS_PER_NODE', unset=NA))
if(is.na(cores)) cores <- detectCores()  
registerDoParallel(cores)

ggplot2::theme_set(ggplot2::theme_bw())
@

% \date{This manuscript was compiled on \today}

\begin{document}

@@

<<data-plot, echo=F, fig.height=6.5, fig.width=6.5, out.width="6.5in", fig.cap = "Weekly measles case reports for 20 UK towns.",fig.show = "hold">>=
library(spatPomp)
x <- he10 <- readRDS("sim/he10.rds")
df <- as.data.frame(x)
df[x@unit_obsnames] <- log10(df[x@unit_obsnames]+1)
unit_nm <- rlang::sym(x@unitname)
df[[unit_nm]] <- factor(df[[unit_nm]], levels = x@unit_names)
g <- ggplot2::ggplot(data = df,
  mapping = ggplot2::aes(x = !!rlang::sym(x@timename),
    y = !!rlang::sym(x@unit_obsnames))) +
  ggplot2::geom_line() +
  ggplot2::facet_wrap(unit_nm)+
  ggplot2::ylab("log10(reported cases)")+
  ggplot2::xlab("Year")
print(g)
@

<<sim-plot, echo=F, fig.height=6.5, fig.width=6.5, out.width="6.5in", fig.cap = "Simulated weekly measles case reports.",fig.show = "hold">>=
library(spatPomp)
x <- sim <- readRDS("sim/sim.rds")
df <- as.data.frame(x)
df[x@unit_obsnames] <- log10(df[x@unit_obsnames]+1)
unit_nm <- rlang::sym(x@unitname)
df[[unit_nm]] <- factor(df[[unit_nm]], levels = x@unit_names)
g <- ggplot2::ggplot(data = df,
  mapping = ggplot2::aes(x = !!rlang::sym(x@timename),
    y = !!rlang::sym(x@unit_obsnames))) +
  ggplot2::geom_line() +
  ggplot2::facet_wrap(unit_nm)+
  ggplot2::ylab("log10(simulated cases)")+
  ggplot2::xlab("Year")
print(g)
@

@@

<<sim-loglik-truth,echo=FALSE>>=
readRDS("w/w1_3/lik.rds") -> w
w6400 <- w[w[,"J"]==6400,]
loglik_truth <- logmeanexp(w6400[,"logLik"],se=TRUE)
@

Before engaging in likelihood maximization, one first wants to validate likelihood evaluation.
Likelihood evaluation for metapopulation models was the main topic of \citet{ionides21} and we do not repeat that analysis here.
In brief, the basic particle filter provides a consistent evaluation of the log-likelihood in a limit where the number of particles is large enough to make the Monte Carlo standard deviation small.
This is practical only when $U$ is small (say, $U\le 5$) but that can be used to calibrate the bias induced by BPF, which turns out to be small for our multi-town measles model when each town is its own block.
It may be surprising that resampling independently on each block (which is what the block particle filter does) is able to capture the dependence.
Heuristically, we note that the dynamic dependence between blocks is maintained by BPF, which updates particles according to the full coupled dynamics.
Whether this is sufficient to obtain a good approximation to the filter distribution is situation-dependent, but for the specific case of metapopulation models (for which the strongest coupling is within units rather than between units) the approximation can be empirically successful.
In principle, the approximation error can be reduced by increasing block size, but in practice the additional Monte Carlo variance acquired by doing this is not worthwhile in situations where the coupling is relatively weak.
The BPF log-likelihood evaluation at the true parameter value is $\loglik_{\mathrm{true}}=\Sexpr{myround(loglik_truth[1],1)}$ with a Monte Carlo standard error of $\Sexpr{myround(loglik_truth[2],1)}$.

@@

<<v6_start,echo=F>>=
readRDS("v4/v1a_3/initial_lik.rds") -> loglik_start
median_start <- median(loglik_start[,"start_loglik"])
@

<<sim_results,echo=F,results=F>>=
library(pomp)
truth_eval <- readRDS("w/w1_3/lik.rds")
truth_loglik<-logmeanexp(truth_eval[truth_eval[,"J"]==25600,"logLik"])
v1a <- read.csv(file="v4/v1a_3/global.csv")
v1b <- read.csv(file="v4/v1b_3/global.csv")
v1c <- read.csv(file="v4/v1c_3/global.csv")
v2a <- read.csv(file="v4/v2a_3/global.csv")
v2b <- read.csv(file="v4/v2b_3/global.csv")
v2c <- read.csv(file="v4/v2c_3/global.csv")
v3a <- read.csv(file="v4/v3a_3/global.csv")
v3b <- read.csv(file="v4/v3b_3/global.csv")
v3c <- read.csv(file="v4/v3c_3/global.csv")
v4a <- read.csv(file="v4/v4a_3/global.csv")
v4b <- read.csv(file="v4/v4b_3/global.csv")
v4c <- read.csv(file="v4/v4c_3/global.csv")
v5a <- read.csv(file="v4/v5a_3/global.csv")
v5b <- read.csv(file="v4/v5b_3/global.csv")
v5c <- read.csv(file="v4/v5c_3/global.csv")
@

<<z3_results,echo=F,results=F>>=
z1a <- read.csv(file="z3/z1a_3/global.csv")
z1b <- read.csv(file="z3/z1b_3/global.csv")
z1c <- read.csv(file="z3/z1c_3/global.csv")
z1d <- read.csv(file="z3/z1d_3/global.csv")
z2a <- read.csv(file="z3/z2a_3/global.csv")
z2b <- read.csv(file="z3/z2b_3/global.csv")
z2c <- read.csv(file="z3/z2c_3/global.csv")
z2d <- read.csv(file="z3/z2d_3/global.csv")
z3a <- read.csv(file="z3/z3a_3/global.csv")
z3b <- read.csv(file="z3/z3b_3/global.csv")
z3c <- read.csv(file="z3/z3c_3/global.csv")
z3d <- read.csv(file="z3/z3d_3/global.csv")
z4a <- read.csv(file="z3/z4a_3/global.csv")
z4b <- read.csv(file="z3/z4b_3/global.csv")
z4c <- read.csv(file="z3/z4c_3/global.csv")
z4d <- read.csv(file="z3/z4d_3/global.csv")
z5a <- read.csv(file="z3/z5a_3/global.csv")
z5b <- read.csv(file="z3/z5b_3/global.csv")
z5c <- read.csv(file="z3/z5c_3/global.csv")
z5d <- read.csv(file="z3/z5d_3/global.csv")
loglik_he <- sum(read.csv("data/he10mle.csv")$loglik)
# -40345.7
@

<<sim_search_boxplot, echo=F, fig.height=4, fig.width=5.5, out.width="5.5in", fig.cap = "Fitting different models to the simulated measles data, using an initial search and four further refinement searches. (A) $4\\times 20$ unit-specific parameters and $9$ shared parameters; (B) $13\\times 20$ unit-specific parameters and no shared parameters. (C) Also all unit-specific, but with immigration rather than coupling, matching the model of He et al (2010). The horizontal dashed line denotes the likelihood obtained by He et al, using \\code{pomp}. Here, $J=4000$, and the random walk standard deviation (on log- and logit-transformed parameters) is 0.005 for the initial search and 0.00125 for subsequent refinements.",fig.show = "hold">>=
a <- cbind(
A1 = v1a$loglik,
A2 = v2a$loglik,
A3 = v3a$loglik,
A4 = v4a$loglik,
A5 = v5a$loglik
)

b <- cbind(
B1 = v1b$loglik,
B2 = v2b$loglik,
B3 = v3b$loglik,
B4 = v4b$loglik,
B5 = v5b$loglik
)

c <- cbind(
C1 = v1c$loglik,
C2 = v2c$loglik,
C3 = v3c$loglik,
C4 = v4c$loglik,
C5 = v5c$loglik
)

loglik_max <- max(cbind(a,b,c),truth_loglik)
boxplot(cbind(a,b,c),ylim=loglik_max-c(200,0),
ylab="Log-likelihood")
abline(h=truth_loglik,lty="dashed",col="blue")
@

<<search_diagnostics, echo=F, fig.height=6.5, fig.width=4.5, out.width="5in", fig.cap = "Three steps of a likelihood search on simulated data (left panels) and UK measles data (right panels). Final log-likelihood values are plotted against starting log-likelihood for an initial search (top row), a refinement of this search (second row) and a second refinement (third row). Starting values for each refinement were 4 copies of the top 25\\% of end points for the previous search. Unit-specific parameters were $\\rho$, $S_0$, $E_0$, $I_0$ (for the simulation study, model A) and all parameters (for the data, model B).">>=
par(mfcol=c(3,2))
par(mai=c(0.3,0.3,0.1,0.1))
par(omi=c(0.3,0.5,0.5,0.1))
##
## (1,1)
##
x <- v1a[,"start_loglik"]
y <- v1a$loglik
x_lim <- range(c(x,truth_loglik,max(y)))
y_lim <- range(c(y,truth_loglik,max(x)))
plot(x,y,xlim=x_lim,ylim=y_lim,
  xlab="",
  ylab="Initial search",
)
abline(a=0,b=1,lty="dashed",col="blue")
abline(h=truth_loglik,lty="dashed",col="blue")
abline(v=truth_loglik,lty="dashed",col="blue")
##
## (2,1)
##
x <- rep(v1a$loglik[1:18],each=2)
y <- v2a$loglik
x_lim <- range(c(x,truth_loglik,max(y)))
y_lim <- range(c(y,truth_loglik,max(x)))
plot(x,y,xlim=x_lim,ylim=y_lim,
  xlab="",
  ylab="1st refinement"
)
abline(a=0,b=1,lty="dashed",col="blue")
abline(h=truth_loglik,lty="dashed",col="blue")
abline(v=truth_loglik,lty="dashed",col="blue")
##
## (3,1)
##
x <- rep(v2a$loglik[1:18],each=2)
y <- v3a$loglik
x_lim <- range(c(x,truth_loglik,max(y)))
y_lim <- range(c(y,truth_loglik,max(x)))
plot(x,y,xlim=x_lim,ylim=y_lim,
    ylab="2nd refinement",
    xlab="Starting log-likelihood"
)
abline(a=0,b=1,lty="dashed",col="blue")
abline(h=truth_loglik,lty="dashed",col="blue")
abline(v=truth_loglik,lty="dashed",col="blue")
##
##
## (1,2)
##
  x <- z1b[,"start_loglik"]
  y <- z1b$loglik
  x_lim <- range(c(x,loglik_he,max(y)))
  y_lim <- range(c(y,loglik_he,max(x)))
  plot(x,y,xlim=x_lim,ylim=y_lim,
    xlab="",
    ylab="",
  )
  abline(a=0,b=1,lty="dashed",col="blue")
  abline(h=loglik_he,lty="dashed",col="blue")
  abline(v=loglik_he,lty="dashed",col="blue")
##
## (2,2)
##
  x <- rep(z1b$loglik[1:18],each=2)
  y <- z2b$loglik
  x_lim <- range(c(x,loglik_he,max(y)))
  y_lim <- range(c(y,loglik_he,max(x)))
  plot(x,y,xlim=x_lim,ylim=y_lim,
    xlab="",
    ylab=""
  )
  abline(a=0,b=1,lty="dashed",col="blue")
  abline(h=loglik_he,lty="dashed",col="blue")
  abline(v=loglik_he,lty="dashed",col="blue")
##
## (3,2)
##
  x <- rep(z2b$loglik[1:18],each=2)
  y <- z3b$loglik
  x_lim <- range(c(x,loglik_he,max(y)))
  y_lim <- range(c(y,loglik_he,max(x)))
  plot(x,y,xlim=x_lim,ylim=y_lim,
    xlab="Starting log-likelihood",
    ylab=""
  )
  abline(a=0,b=1,lty="dashed",col="blue")
  abline(h=loglik_he,lty="dashed",col="blue")
  abline(v=loglik_he,lty="dashed",col="blue")

LINE<-0.25
CEX <- 0.9
mtext("Initial search",side=2,line=LINE,outer=TRUE,at=0.833,cex=CEX)
mtext("First refinement",side=2,line=LINE,outer=TRUE,at=0.5,cex=CEX)
mtext("Second refinement",side=2,line=LINE,outer=TRUE,at=0.167,cex=CEX)
mtext("Simulated data",side=3,line=LINE,outer=TRUE,at=0.25,cex=CEX)
mtext("UK towns",side=3,line=LINE,outer=TRUE,at=0.75,cex=CEX)
mtext("Log-likelihood",side=1,line=LINE,outer=TRUE,at=0.25,cex=CEX)
mtext("Log-likelihood",side=1,line=LINE,outer=TRUE,at=0.75,cex=CEX)

@

@@

<<data_search_boxplot, echo=F, fig.height=4, fig.width=5.5, out.width="5.5in", fig.cap = "Fitting different models to the UK measles data using the method tested on simulated data. (A) $4\\times 20$ unit-specific parameters and $9$ shared parameters; (B) $13\\times 20$ unit-specific parameters and no shared parameters. (C) Also all unit-specific, but with immigration rather than coupling, matching the model of He et al (2010). The horizontal dashed line denotes the likelihood obtained by He et al, using \\code{pomp}.",fig.show = "hold">>=
a <- cbind(
A1 = z1a$loglik,
A2 = z2a$loglik,
A3 = z3a$loglik,
A4 = z4a$loglik,
A5 = z5a$loglik
)

b <- cbind(
B1 = z1b$loglik,
B2 = z2b$loglik,
B3 = z3b$loglik,
B4 = z4b$loglik,
B5 = z5b$loglik
)

c <- cbind(
C1 = z1c$loglik,
C2 = z2c$loglik,
C3 = z3c$loglik,
C4 = z4c$loglik,
C5 = z5c$loglik
)

d <- cbind(
D1 = z1d$loglik,
D2 = z2d$loglik,
D3 = z3d$loglik,
D4 = z4d$loglik,
D5 = z5d$loglik
)
loglik_max <- max(cbind(a,b,c),loglik_he)
boxplot(cbind(a,b,c),ylim=loglik_max-c(5500,0),
  ylab="Log-likelihood")
abline(h=loglik_he,lty="dashed",col="blue")
@

Fig.~\ref{fig:data_search_boxplot} shows results for fitting models A, B and C to UK measles data using successive rounds of {\ibpf}, applying the same method used for the simulation study shown in Fig.~\ref{fig:sim_search_boxplot}.
The dashed lines show the sum of the log-likelihoods obtained by \citet{he10}, $\ell_{\mathrm He}=\Sexpr{myround(loglik_he,1)}$.
The value $\ell_{\mathrm He}$ corresponds to model C.
BPF with each town forming a separate block, applied to an uncoupled model such as C, is equivalent to carrying out independent particle filters for each unit.
Indeed, if the published parameter values from \citet{he10} are inserted into the \code{spatPomp} object for model C, then the \code{bpfilter()} function can be used to carry out BPF, which retrieves $\ell_{\mathrm He}$, up to Monte Carlo error.
Each of models A, B and C in Fig.~\ref{fig:data_search_boxplot} shows shortfall relative to $\ell_{\mathrm He}$.

@@

<<spatreg_boxplot, echo=F, fig.height=4, fig.width=5.5, out.width="5.5in", fig.pos="h", fig.cap = paste0("Varying the spatial autoregression algorithmic parameter for shared parameters with simulated measles data. The log-likelihood was obtained using $M=100$ iterations of IBPF starting at random parameters (median starting log-likelihood, ",signif(median_start,3), "). The horizontal dashed line denotes the log-likelihood at the true parameters.")>>=
loglik_truth <- -38882.7 # from w1.r
spat_regression <- c(0, 1/64, 1/32, 1/16, 1/8, 1/4, 1/2, 1) 
spat_regression_char <- c("0", "1/64", "1/32", "1/16", "1/8", "1/4", "1/2", "1")
Experiment <- length(spat_regression)
results <- foreach(experiment=1:Experiment,.combine=rbind) %do% {
  r <- readRDS(file=paste0("v/v6_3/global_e",experiment,".rds"))
  cbind(r,sp_reg=spat_regression[experiment])
}
loglik_max <- max(c(loglik_truth,results$loglik))
results <- as.data.frame(results)
boxplot(loglik~sp_reg,data=results,ylim=c(-40000,loglik_max),
  ylab="Log-likelihood", xlab="spatial autoregression parameter",
  names=spat_regression_char)
abline(h=loglik_truth,col="blue",lty="dotted")
@

>>>>

\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{xcolor}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

@@

% \date{This manuscript was compiled on \today}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{figure}

\includegraphics[width=6.5in]{figure/data-plot-1} \hfill{}

\caption[Weekly measles case reports for 20 UK towns]{Weekly measles case reports for 20 UK towns.}\label{fig:data-plot}
\end{figure}

\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{figure}

\includegraphics[width=6.5in]{figure/sim-plot-1} \hfill{}

\caption[Simulated weekly measles case reports]{Simulated weekly measles case reports.}\label{fig:sim-plot}
\end{figure}

\end{knitrout}

@@

Before engaging in likelihood maximization, one first wants to validate likelihood evaluation.
Likelihood evaluation for metapopulation models was the main topic of \citet{ionides21} and we do not repeat that analysis here.
In brief, the basic particle filter provides a consistent evaluation of the log-likelihood in a limit where the number of particles is large enough to make the Monte Carlo standard deviation small.
This is practical only when $U$ is small (say, $U\le 5$) but that can be used to calibrate the bias induced by BPF, which turns out to be small for our multi-town measles model when each town is its own block.
It may be surprising that resampling independently on each block (which is what the block particle filter does) is able to capture the dependence.
Heuristically, we note that the dynamic dependence between blocks is maintained by BPF, which updates particles according to the full coupled dynamics.
Whether this is sufficient to obtain a good approximation to the filter distribution is situation-dependent, but for the specific case of metapopulation models (for which the strongest coupling is within units rather than between units) the approximation can be empirically successful.
In principle, the approximation error can be reduced by increasing block size, but in practice the additional Monte Carlo variance acquired by doing this is not worthwhile in situations where the coupling is relatively weak.
The BPF log-likelihood evaluation at the true parameter value is $\loglik_{\mathrm{true}}=-40612.5$ with a Monte Carlo standard error of $0.6$.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{figure}

\includegraphics[width=5.5in]{figure/sim_search_boxplot-1} \hfill{}

\caption[Fitting different models to the simulated measles data, using an initial search and four further refinement searches]{Fitting different models to the simulated measles data, using an initial search and four further refinement searches. (A) $4\times 20$ unit-specific parameters and $9$ shared parameters; (B) $13\times 20$ unit-specific parameters and no shared parameters. (C) Also all unit-specific, but with immigration rather than coupling, matching the model of He et al (2010). The horizontal dashed line denotes the likelihood obtained by He et al, using \code{pomp}. Here, $J=4000$, and the random walk standard deviation (on log- and logit-transformed parameters) is 0.005 for the initial search and 0.00125 for subsequent refinements.}\label{fig:sim_search_boxplot}
\end{figure}

\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{figure}

\includegraphics[width=5in]{figure/search_diagnostics-1} \hfill{}

\caption[Three steps of a likelihood search on simulated data (left panels) and UK measles data (right panels)]{Three steps of a likelihood search on simulated data (left panels) and UK measles data (right panels). Final log-likelihood values are plotted against starting log-likelihood for an initial search (top row), a refinement of this search (second row) and a second refinement (third row). Starting values for each refinement were 4 copies of the top 25\% of end points for the previous search. Unit-specific parameters were $\rho$, $S_0$, $E_0$, $I_0$ (for the simulation study, model A) and all parameters (for the data, model B).}\label{fig:search_diagnostics}
\end{figure}

\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{figure}

\includegraphics[width=5.5in]{figure/data_search_boxplot-1} \hfill{}

\caption[Fitting different models to the UK measles data using the method tested on simulated data]{Fitting different models to the UK measles data using the method tested on simulated data. (A) $4\times 20$ unit-specific parameters and $9$ shared parameters; (B) $13\times 20$ unit-specific parameters and no shared parameters. (C) Also all unit-specific, but with immigration rather than coupling, matching the model of He et al (2010). The horizontal dashed line denotes the likelihood obtained by He et al, using \code{pomp}.}\label{fig:data_search_boxplot}
\end{figure}

\end{knitrout}

Fig.~\ref{fig:data_search_boxplot} shows results for fitting models A, B and C to UK measles data using successive rounds of {\ibpf}, applying the same method used for the simulation study shown in Fig.~\ref{fig:sim_search_boxplot}.
The dashed lines show the sum of the log-likelihoods obtained by \citet{he10}, $\ell_{\mathrm He}=-40345.7$.
The value $\ell_{\mathrm He}$ corresponds to model C.
BPF with each town forming a separate block, applied to an uncoupled model such as C, is equivalent to carrying out independent particle filters for each unit.
Indeed, if the published parameter values from \citet{he10} are inserted into the \code{spatPomp} object for model C, then the \code{bpfilter()} function can be used to carry out BPF, which retrieves $\ell_{\mathrm He}$, up to Monte Carlo error.
Each of models A, B and C in Fig.~\ref{fig:data_search_boxplot} shows shortfall relative to $\ell_{\mathrm He}$.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{figure}[h]

\includegraphics[width=5.5in]{figure/spatreg_boxplot-1} \hfill{}

\caption[Varying the spatial autoregression algorithmic parameter for shared parameters with simulated measles data]{Varying the spatial autoregression algorithmic parameter for shared parameters with simulated measles data. The log-likelihood was obtained using $M=100$ iterations of IBPF starting at random parameters (median starting log-likelihood, -40800). The horizontal dashed line denotes the log-likelihood at the true parameters}\label{fig:spatreg_boxplot}
\end{figure}

\end{knitrout}
